\documentclass[12pt,reqno]{amsart}
\usepackage[margin = 1.35 in]{geometry}
\usepackage[frenchmath,defaultmathsizes]{mathastext}
\usepackage{
  hyperref,
  amsmath,
  amssymb,
  tikz,
  amsthm,
  thmtools,
  microtype,
  enumitem,
  stmaryrd,
  tikz-cd,
  mathrsfs,
}
\usepackage{graphicx}


\linespread{1.1}
\usepackage[all]{xy}
\usepackage{eucal}

\title{Counting Cubic Surfaces}
\author{Anand Deopurkar, Anand Patel
  \& Dennis Tseng}




%-----------------------------------------------
\def\labelitemi{--}
\newcommand{\todo}[1]{\fbox{ToDo: #1}}
\renewcommand{\k}{k}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\Bl}{Bl}
\DeclareMathOperator{\Br}{Br}
\DeclareMathOperator{\ProjBun}{ProjBun}
\renewcommand{\Vec}{\operatorname{Vec}}
\DeclareMathOperator{\Polar}{Polar}
\DeclareMathOperator{\res}{Res}
\DeclareMathOperator{\Pole}{Pole}
\DeclareMathOperator{\Hilb}{Hilb}
\DeclareMathOperator{\Sing}{Sing}
\DeclareMathOperator{\Orb}{Orb}
\DeclareMathOperator{\M}{\mathcal{M}}
\newcommand{\cO}{{\mathcal O}}
\renewcommand{\to}{{\longrightarrow}}

\renewcommand{\sectionautorefname}{\S}
\renewcommand{\subsectionautorefname}{\S}
\input{macros}
\declaretheorem[sibling=theorem,style=remark]{remark}
\numberwithin{equation}{section}
\declaretheorem[title=Theorem]{maintheorem}
\renewcommand{\themaintheorem}{\Alph{maintheorem}}


\renewcommand{\O}{\mathcal O}
\newcommand{\G}{\mathbf G}
\newcommand{\td}{\widetilde}
\newcommand{\Frac}{{\mathrm{Frac}}\,}
\newcommand{\Jac}{{\textrm{Jac}}}
\DeclareMathOperator{\Ram}{Ram}
\newcommand{\Hdg}{\overline{\H}_{d,g}}
\newcommand{\Hdgn}{\overline{\H}_{d,g}}
\newcommand{\Hdgnt}{\overline{\H}_{d,g}^{(2)}}
\newcommand{\Hdgnth}{\overline{\H}_{d,g}^{(3)}}
\newcommand{\sfT}{\mathcal T}
\newcommand{\sfD}{\mathcal D}
\newcommand{\sfB}{\mathcal B}
\newcommand{\V}{\mathcal V}
\newcommand{\cP}{\mathcal P}
\newcommand{\fm}{\mathfrak m}
\newcommand{\smvee}{\raise0.5ex\hbox{$\scriptscriptstyle\vee$}}

\newcommand{\compl}[1]{\widehat{#1}}
\newcommand{\Spec}{{\text{\rm Spec}\,}}
\newcommand{\Spf}{{\text{\rm Spf}\,}}
\renewcommand {\o}[1]{\overline{#1}}
\newcommand{\Proj}{{\text{\rm Proj}\,}}
\newcommand{\git}{\sslash}
% -----------------------------------------------

%%% BEGIN DOCUMENT

\begin{document}




\maketitle

\section{Introduction}
\label{sec:intro}

Cubic surfaces have held the attention of mathematicians ever since
1849, when Cayley and Salmon demonstrated the existence of the $27$
lines.  Our aim in this paper is to add to this long history by
establishing an enumerative formula which counts the number of times a
general cubic surface's moduli occurs in any suitably general
$4$-parameter family of cubic surfaces. Applying this formula to a few
examples yields:
\begin{enumerate}
\item[(A)] \label{fact:RanestadSturmfelds} {\sl A general cubic surface
    arises $96120$ times in a general $4$ dimensional linear system of
    cubic surfaces,} and
\item[(B)] {\sl A general cubic surface arises $42120$ times as a
    hyperplane section of a general cubic threefold.}
\end{enumerate}

\begin{theorem}\label{theorem:main}
  Let $\pi: X \to B$ be a good family of cubic surfaces over a
  proper base $B$ and whose generic fiber is smooth. If
  $v_{i}, i=1, 2,3, 4$ denote the Chern classes of the rank $4$ vector
  bundle $\V = \pi_{*}(\omega_{\pi}^{-1})$, then
  \begin{align}
    \label{eq:MAIN}
   \int_{B} 1080v_{1}^{2}v_{2} - 1080v_{1}v_{3}+9720v_{4} = \deg \mu,
  \end{align}
  where $\mu: B \dashrightarrow \M$ is the induced map to the moduli
  space of cubic surfaces.
\end{theorem}

The exact notion of a good family can be found in
\autoref{sec:good-families}.  We simply mention here that it includes
the case where all fibers are semi-stable cubic surfaces (in the sense
of GIT), and the relative dualizing sheaf $\omega_{\pi}$ exists and is
a line bundle.

The formula has a curious corollary:

\begin{corollary}
  \label{cor:ineq} If $\pi: X \to B$ is a good family of cubic
  surfaces parametrized by a $4$ dimensional proper variety $B$,
  then $$\int_{B} v_{1}^{2}v_{2} - v_{1}v_3 + 9v_{4} \geq 0$$ with
  equality holding if and only if a general cubic surface does not
  arise as a fiber.
\end{corollary}



\subsection{Strategy}
\label{sec:strategy}

The overall strategy of the proof is quite simple: We argue that a
priori there exists a formula of the form

\begin{align}
  \label{eq:P}
  \int_{B} a_{1^4}v_{1}^{4} + a_{1^{2}2}v_{1}^{2}v_{2} + a_{13}v_{1}v_{3} + a_{2^2}v_{2}^{2} + a_{4}v_{4} = \deg \mu,
\end{align}
as in the statement of \autoref{theorem:main} -- this is merely an
instance of a foundational theorem in equivariant enumerative geometry
\cite[].  Then, we determine the five coefficients $a_{\bullet}$ by
exhibiting several good families for which we know all $v_{i}$ {\sl
  and} $\deg \mu$.  In this way, we obtain a system of linear
equations in the five unknowns $a_{\bullet}$, which turns out to have
a unique solution.  In fact, we exhibit nine(?)  such
families/equations; the redundancy provides extra checks on the end
result.
  

\subsection{History and context}
\label{sec:context}

The enumerative problem (A) was first mentioned in print in
K. Ranestad and B. Sturmfeld's \cite[], and the number $96120$ was
first arrived at by \cite[] using numerical methods, though the method
was one verification short of constituting a proof.  R. Laza brought
(B) to the first two authors' attention during a meeting at
Oberwolfach in 2017.


\autoref{theorem:main} represents a frontier case of a much more
substantial and ongoing enumerative story, which we briefly advertise
here. If $E$ is an $n+1$ dimensional vector space and if
$F \in \Sym^dE^{\smvee}$ is a non-zero degree $d$ homogeneous form on
$E$, then we let $$\Orb(F) \subset \P \Sym^d E^{\smvee}$$ denote the
closure of the $\GL(E)$-orbit of the point
$[F] \in \P \Sym^{d}E^{\smvee}$.  Simple questions about the geometry
of the variety $\Orb(F)$, and its relationship to the geometry of the
hypersurface defined by $F$, remain unanswered.  Here, perhaps the
most well-studied problem is {\sl the calculation of the degree of the
  orbit-closure $\Orb(F)$}.  Aluffi and Faber, in a series of
remarkable papers \cite[], initially brought attention to this
enumerative problem and completely solved it when $n=1, 2$ and $d$ 
arbitrary.

We propose a slight shift in perspective on the problem: We should
instead aim to compute the {\sl equivariant fundamental class} of the
orbit closure, denoted
$$[\Orb(F)] \in A_{\GL(E)}^{\bullet}(\P \Sym^{d}E^{\smvee}).$$
This class not only determines the degree of the orbit closure, but
also tracks many more enumerative problems like (B).  As is
demonstrated in the appendix \cite[], \autoref{theorem:main} contains
the same content as the calculation of this equivariant class when $F$
is assumed to be a {\sl general} degree $3$ form in four variables.

This change in perspective opens up our avenue of attack.  As will be
seen in \autoref{section:???} we exploit certain {\sl isotrivial}
families of cubic surfaces to obtain quick relations on the
coefficients $a_{\bullet}$.  In order to justify the use of these
isotrivial families, it is necessary to know whether a cubic surface
is represented by a point in the closure of $\Orb(F)$, with $F$
general.  This is an instance of the much more general ``Orbit Closure
Problem'' \cite[].






\section{Preliminaries}
\label{sec:good}

After establishing notation, conventions, and classical facts about
cubic surfaces, this section introduces the notion of a {\sl good}
family of cubic surfaces and then provides the main tool
(\autoref{prop:good}) for verifying the goodness of several families
occurring in the paper.


\subsection{Notation and conventions}
\label{sec:notation-conventions}
All schemes are assumed of finite-type over an algebraically closed,
characteristic zero field, $\k$. If $\pi: X \to Y$ is a map of schemes
and if $y \in Y$ is a point, then we let $X_y$ denote the fiber scheme
$\pi^{-1}(y)$, and if both $X$ and $Y$ have dualizing line bundles
$\omega_{X}, \omega_{Y}$ respectively, then we write $\omega_{X/Y}$,
or $\omega_{\pi}$, for the line bundle
$\omega_{X} \otimes \pi^{*}\omega_{Y}^{-1}$.  If $\mathcal{A}$ is a
vector bundle, then we let $\P \mathcal{A}$ denote its
projectivization, which parametrizes $1$-dimensional {\sl subspaces}
in the fibers of $\mathcal{A}$.

If a smooth conic $C \subset \P^{2}$ is given, and if $p \in \P^{2}$
is any point, we let $\Polar(p)$ denote the line polar to $p$ with
respect to $C$.  Similarly, if $L \subset \P^{2}$ is any line, we let
$\Pole(L)$ denote the point polar to $L$.




\subsection{Classical facts about cubic surfaces}
\label{sec:classical-facts}

\begin{theorem}[Cayley, Salmon]
  \label{theorem:cayleysalmon} Every smooth cubic surface contains
  exactly $27$ lines.
\end{theorem}

An ordered tuple of six lines $(\ell_1, \dots, \ell_6)$ on a cubic
surface is called a {\sl six} if they are pairwise disjoint.  An
unordered pair of sixes
$\{(\ell_1, \dots, \ell_6), (\ell_1', \dots, \ell_6')\}$ is called a
{\sl double-six} if
\begin{itemize}
\item $\ell_{i}$ and $\ell'_{i}$ are disjoint for all $i$, and
\item $\ell_{i}$ and $\ell'_{j}$ meet at a point whenever $i \neq j$.
  \end{itemize}

\begin{theorem}[Schl\"{a}fli]
  \label{theorem:schlafli} Each six on a smooth cubic surface has a
  unique extension to a double-six, and every smooth cubic surface
  contains $36$ double-sixes.
\end{theorem}

\subsubsection{Moduli spaces of cubic surfaces}
\label{sec:modulispacescubic}
We let $\M$ denote the {\sl coarse moduli space of cubic surfaces},
obtained by taking the GIT quotient of the linear system of cubic
surfaces in $\P^3$ by the action of $\Aut(\P^3) = \PGL_{4}(\k)$. By
the classical calculation of invariants \cite[], we know that $\M$ is
a $4$ dimensional variety isomorphic to the weighted projective space
$\P(1,2,3,4,5)$.

We let $\M^{\dagger}$ denote the {\sl moduli space
  of marked cubic surfaces} which parametrizes pairs
$(S, \underline{\ell})$ where $\underline{\ell}$ is a six on a smooth
cubic surface $S \subset \P^3$, taken up to the action of
$\Aut(\P^3)$.  There is a natural quasi-finite, dominant forgetful
morphism
\begin{align}
  \label{eq:modulispaces}
  \sigma: \M^{\dagger} \to \M\\
  (S, \underline{\ell}) \mapsto S. \nonumber
\end{align}

\autoref{theorem:schlafli} implies that
\begin{align}
  \label{eq:degreesigma}
  \deg (\sigma) = 72 \times 6! = 51840.
\end{align}


\subsection{Good families}
\label{sec:good-families}

Let $E$ denote a four dimensional $\k$-vector space, and hereafter fix
a {\sl general} degree $3$ form $F \in \Sym^{3}E^{\smvee}$.  Let
$$\Orb(F) \subset \P \Sym^{3}E^{\smvee} \simeq \P^{19}$$
denote the $\GL(E)$-orbit closure of the point $[F]$.  We let
$$\partial \Orb(F) = \Orb(F) \setminus \GL(E) \cdot [F]$$
denote the {\sl boundary}, i.e. the complement of the orbit of $[F]$
in its closure. $\Orb(F)$ is a $15$ dimensional variety whose singular
locus lies in the proper subvariety $\partial \Orb(F)$.  

\begin{definition}
\label{def:goodfamily}
Let $\pi :X \to B$ be a flat, projective morphism of relative
dimension $2$, with $B$ a $4$-dimensional scheme. We say $\pi$ is {\sl
  a good family of cubic surfaces} if:
\begin{itemize}
\item There exists a $\P^3$-bundle $\rho: P \to B$ and a closed
  embedding $\iota: X \hookrightarrow P$ embedding each fiber $X_b$ as
  a cubic surface in $P_b$ and $\pi = \rho \circ \iota$,
\item $X_{b}$ is reduced and irreducible for all $b \in B$, and
\item There is {\sl no} $b \in B$ such that the cubic surface $X_b$ is
  represented by a point in $\partial \Orb(F) \subset \P^{19}$.
\end{itemize}
\end{definition}

The base $B$ of a good family carries the {\sl natural} rank $4$
vector bundle
\begin{align}
  \label{eq:V}
  \V := \pi_{*}\omega_{X/B}^{-1}.
\end{align}
Furthermore, assuming the general fiber of $\pi$ is smooth, $B$ admits
a rational map
\begin{align}
  \label{eq:mu}
  \mu: B \dashrightarrow \M
\end{align}
to the coarse moduli variety of cubic surfaces
$\mathcal{M} := \Sym^{3}E^{\smvee} \sslash GL(E)$.




\begin{definition}
  \label{def:admissible} A length $6$ subscheme $Z \subset \P^{2}$
  with ideal sheaf $\mathcal{I}_{Z}$ is {\sl admissible} if:
  \begin{enumerate}
  \item $Z$ is curvilinear, i.e $Z$ is contained in a smooth curve,
  \item $h^{0}(\mathcal{I}_Z(3)) = 4$, and
  \item $Z$ is the scheme cut out by the vector space of cubics
    $H^0(\P^2, \mathcal{I}_Z(3))$.
  \end{enumerate}
\end{definition}

\begin{definition}
  \label{def:cubicZ} Let $Z \subset \P^2$ be an admissible length $6$
  subscheme.  The {\sl cubic surface associated to $Z$}, denoted
  $X_Z \subset \P^3$ is the image of the anti-canonical map
  $\kappa: \Bl_{Z}\P^2 \to \P^3$ induced by the linear system
  $H^0(\P^2,\mathcal{I}_Z(3))$.
\end{definition}

\begin{proposition}
  \label{prop:good} Let $Z \subset \P^2$ be an admissible, length $6$
  subscheme with $X_Z \subset \P^3$ its associated cubic surface. Then
  $\dim Aut(\P^2,Z) > 0$ if and only if $\dim Aut(\P^3,X_Z) > 0$.
\end{proposition}

\begin{proof} The implication
  $\dim Aut(\P^2,Z) > 0 \implies \dim Aut(\P^3,X_Z) > 0$ is simpler:
  Any automorphism $g \in Aut(\P^2,Z)$ naturally lifts to an
  automorphism $g' \in \Aut \Bl_{Z}\P^2$. This latter automorphism
  must preserve the anti-canonical line bundle
  $\omega_{\Bl_{Z}(\P^2)}^{-1}$, and therefore induces an element in
  $Aut(\P^3, X_Z)$. This element is nontrivial if $g$ is, because
  $\kappa: \Bl_{Z}(\P^2) \to X_Z$ is birational. The implication
  follows.


  The opposite implication
  $\dim Aut(\P^3,X_Z) > 0 \implies \dim Aut(\P^2,Z) > 0$ is more
  intricate. First, note that $\Bl_{Z}\P^2$ is a surface with finitely
  many $A_n$ singularities, thanks to the curvilinearity of $Z$; let
  $\tau: Y \to \Bl_{Z}\P^2$ denote its minimal desingularization.
  Since $A_n$ singularities are canonical, we conclude that
  $\tau^{*}(\omega_{\Bl_{Z}\P^2}) = \omega_{Y}$.  The composite
  $\kappa':= \kappa \circ \tau: Y \to X_{Z}$ can only contract a curve
  $C \subset Y$ to a singular point of $X_Z$.  This follows because   
  $\kappa'^{*}\omega_{X_{Z}} = \omega_{Y}$. Thus,
  $\kappa': \kappa'^{-1}(X_{Z}^{sm}) \to X_{Z}^{sm}$ is an
  isomorphism. Our claim is that $\kappa':Y \to X_{Z}$ is also the
  minimal desingularization of $X_Z$.

  Since $Y$ is {\sl some} desingularization of $X_Z$,
  $\kappa':Y \to X_{Z}$ factors through the minimal desingularization
  $\widetilde{X_{Z}} \to X_{Z}$ of $X_{Z}$; let
  $\alpha: Y \to \widetilde{X_{Z}}$ denote the induced map. $\alpha$
  is a birational morphism between smooth surfaces. Therefore, if it
  is not biregular, there must be a smooth $(-1)$ rational curve
  $E \subset Y$ contracted by $\alpha$.  Since $\omega_{Y}$ is pulled
  back from $\widetilde{X_{Z}}$, it follows that $\omega_{Y}|_{E}$ is
  trivial. This, along with $E \cdot E = -1$, contradicts the
  adjunction formula.  Hence $\alpha$ is an isomorphism.

  Every automorphism of a surface lifts uniquely to its minimal
  desingularization. Therefore, if $\dim Aut(\P^3,X_Z) >0 $, it
  follows that $\dim Aut(Y) >0$. Under this assumption, let
  $G \subset \Aut(Y)$ denote the connected component containing
  identity.

  The Picard group $Pic(Y)$ is discrete, so the connected group $G$
  acts trivially on $Pic(Y)$.  In particular, the line bundle $L$ on
  $\Bl_{Z}\P^2$ inducing the morphism $Y \to \Bl_{Z}\P^2 \to \P^2$ is
  preserved by $G$. Therefore, $G$ induces an action on
  $\P H^0(Y,L)= \P^2$.  This action renders the blow-down map
  $\Bl_{Z}\P^2 \to \P^2$ $G$-equivariant, from which it follows that
  the action of $G$ on $\P^2$ preserves the subscheme $Z$, which is
  what we sought to show.

  
\end{proof}




\section{Family $B_1$}
\label{sec:first-test-family}

In this section, we construct a good family over $B_{1} = \P^{4}$.
Let $S$ denote the blow up of $\P^{2}$ at two points $y_1,y_2$. We let
$E_{1}, E_{2}$ denote the corresponding exceptional lines on $S$ and
we let $L \subset S$ denote the proper transform of a line in $\P^2$
passing through the two points $y_1,y_2$. Finally, we pick a general
conic through $y_{2}$ and let $C \subset S$ denote its proper
transform. Let $\omega_{S}^{-1}$ denote the anti-canonical line bundle
on $S$.  

\subsection{Construction of $B_1$}
\label{sec:construction-b_1}


The base of our first family is
\begin{align}
  \label{eq:B1}
  B_1 := \Hilb^{4}C \simeq \P^{4}.
\end{align}
$B_1$ carries a good family of cubic surfaces over it.  In short, to
each degree $4$ divisor $Z \subset C$, we assign the cubic surface
$X_{Z}$ which is the image of $\Bl_{Z}S$ under its anti-canonical
map. The following proposition justifies this construction:

\begin{proposition}
  \label{prop:B1} Let $Z \subset S$ be any length $4$ subscheme of $C$
  with ideal sheaf $\mathcal{I}_{Z} \subset \mathcal{O}_{S}$. Then
  \begin{enumerate}
  \item $h^{0}(S, \mathcal{I}_{Z} \otimes \omega_{S}^{-1}) = 4$, and
  \item $Z \subset S$ is the subscheme defined by the vector space of
    sections $H^{0}(S, \mathcal{I}_{Z} \otimes \omega_{S}^{-1})$.
  \end{enumerate}
\end{proposition}

\begin{proof}
  We translate (1) and (2) into geometric statements about the
  anti-canonical embedding $S \subset \P^{7}$.  The line bundle
  $\omega_{S}^{-1}(-C)$ on $S$ is basepoint free, as its divisor class
  is represented by proper transforms of lines through
  $y_{1} \in \P^2$, which become separated in the blow up.  The
  geometric consequence of this is: {\sl If
    $\langle C \rangle \simeq \P^5 \subset \P^7$ is the linear span of
    $C$, then $\langle C \rangle \cap S = C$, scheme theoretically.}

  Now $C$ is a rational normal quintic curve in its span
  $\langle C \rangle$. The following is a basic fact about rational
  normal curves: {\sl Every length $m \leq n$ subscheme of rational
    normal curve of degree $n$ spans a linear space of dimension $m-1$
    which, in turn, intersects the rational normal curve precisely at
    the length $m$ scheme.}  Both (1) and (2) follow directly from
  this.
\end{proof}

Let $\mathcal{Z} \subset B_1 \times C$ denote the universal
length $4$ subscheme, and consider $\mathcal{Z}$ as a closed subscheme
of the product $B_1 \times S$. Let $\pi_{1}, \pi_{2}$ denote the
projections of $B_1 \times S$ to its respective factors.
Then we set
\begin{align}
  \label{eq:X1}
  X' := \Bl_{\mathcal{Z}} \left( B_1 \times S \right).
\end{align}
Abusing notation, we continue to let $\pi_{1}$ and $\pi_{2}$ denote
the natural maps from $X'$ to $B_1$ and $S$, respectively.  We
let $E \subset X'$ denote the exceptional divisor over $\mathcal{Z}$.


Consider the line bundle
$\mathcal{L} := \pi_{2}^{*}\omega_{S}^{-1} (-E) =
\omega_{X'/B_{1}}^{-1}$ on $X'$.  By \autoref{prop:B1},
\begin{align}
  \label{eq:V1}
  \V := \pi_{1 *}\mathcal{L}
\end{align}
is a rank $4$ vector bundle on $B_1$, and the canonical evaluation map
\begin{align}
  \label{eq:eval1}
  \pi_{1}^{*}\V \to \mathcal{L}
\end{align}
is surjective.  Therefore, we obtain a map
\begin{align}
  \label{eq:X11}
  \kappa: X' \to \P \V^{\smvee}
\end{align}
whose image $X := \kappa(X')$ is a family of cubic surfaces
parametrized by $B_1$.  Let $\pi: X \to B_1$ denote the natural map.
By tracing through the construction, one can see that the vector
bundle $\V$ is equal to $\pi_{*} \omega_{X/B_1}'$, i.e. $\V$ is the
natural bundle for $\pi: X \to B_1$.

\subsection{Chern classes of $\V$}
\label{sec:chern-classes-b_1}

In order to calculate the Chern classes of $\V$, we express it as an
extension of a trivial rank $2$ vector bundle by the Lazarsfeld-Mukai
bundle on $B_1$ associated to the line bundle
$\omega_{S}^{-1}|_{C}$. By identifying the conic $C$ with $\P^{1}$,
this latter line bundle is $\O_{\P^{1}}(5)$ -- we will switch back and
forth between $C$ and $\P^{1}$ in what follows.  We also identify
$B_{1}$ with $\P^{4}$.


The trivial sub-bundle of $\V$ arises as follows: The fiber $\V_{[Z]}$
over a point $[Z] \in B_1$, corresponding to a subscheme
$Z \subset C$, is the vector space
$H^{0}(S, \mathcal{I}_{Z} \otimes \omega_{S}^{-1})$.  The latter
vector space contains the fixed $2$ dimensional vector space
$H^{0}(S, \omega_{S}^{-1}(-C))$.  This yields a $2$-dimensional
trivial subbundle of $\V$, whose quotient we denote by $\mathcal{K}$.


The bundle $\mathcal{K}$ is naturally identified with the kernel in
the exact sequence
\begin{align}
  \label{eq:LM}
  0 \to \mathcal{K} \to H^{0}(\P^1, \O_{\P^{1}}(5)) \otimes \O_{\P^4} \to \O_{\P^{1}}(5)^{[4]} \to 0 
\end{align}

Here, the rank four bundle $\O_{\P^{1}}(5)^{[4]}$ is the tautological
bundle whose fiber over a point $[Z] \in B_{1}$, corresponding to a
length $4$ subscheme $Z \subset \P^{1}$, is the vector space
$H^{0}(Z, \O_{\P^{1}}(5)|_{Z})$.  The map on the right side of
\eqref{eq:LM} is simply restriction of sections.

It is an easy exercise to show that
$\mathcal{K} \simeq \O_{\P^{4}}(-1) \oplus \O_{\P^{4}}(-1)$.  The
following lemma summarizes the relevant Chern class computations of
$\V$ -- for brevity's sake, we equate a $0$-cycle with its degree.

\begin{lemma}
  \label{lemma:chernB1}
  For the natural bundle $\V$ over $B_1= \P^{4}$, we have:
  \begin{align}\nonumber
    v_{1}^{4} = 16,\\\nonumber
    v_{1}^{2}v_{2} = 4,\\\nonumber
    v_{1}v_{3} =0,\\\nonumber
    v_2^{2} = 1,\\\nonumber
    v_{4} = 0.
  \end{align}
\end{lemma}

\begin{proof}
  By the Whitney sum formula, the Chern classes of $\V$ are
  $v_{1} = -2h$, $v_{2}=h^2$, and $v_{3}= v_{4}=0$, where $h$ denotes
  the hyperplane class on the projective space $B_1 = \P^{4}$.
\end{proof}









\subsection{Enumerating cubics in $B_1$}
\label{sec:enum-cubics-b_1}


For $B_1$ to be of any use, we must {\sl a priori} know the degree of
the map to moduli $\mu: B_1 \dashrightarrow \M$.  First note that
$\mu$ factors through the quasi-finite, degree
$72 \times \frac{6!}{4!}$ cover $\M^{\dagger}/S_{4} \to \M$.  Here,
the symmetric group $S_4$ acts by permuting the last four lines in a
six $(\ell_{1}, \dots, \ell_{6})$ on a cubic surface.


The moduli map $\mu: B_{1} \dashrightarrow \M$ naturally factors
through a map $\mu': B_1 \dashrightarrow \M^{\dagger}/S_{4}$ by
sending a general subscheme $Z \subset C$ to the marked cubic surface
$(\Bl_{Z}S, E_1, E_2, E_{Z})$. Here, $E_Z$ denotes the union of four
exceptional lines above the points of $Z$.


Thus, in order to compute $\deg \mu$, we merely need to compute
$\deg \mu'$.

  \begin{lemma}
    \label{lemma:degreemudaggerB1}
    $\mu': B_1 \dashrightarrow \M^{\dagger}/S_{4}$ has degree $2$.
  \end{lemma}

  \begin{proof}
    Beginning with a general marked cubic surface
    $(X, \ell_{1}, \ell_2, \dots, \ell_{6})$ we can blow down the six
    to produce a map $\varphi: X \to \P^2$. The map $\varphi$ is only
    well-defined up to the action of $\Aut(\P^{2})$.  By composing
    with an automorphism, we may assume that
    $\varphi(\ell_{1}) = y_{1}$ and $\varphi(\ell_{2}) = y_{2}$.

    The $4$ dimensional subgroup $H \subset \Aut(\P^{2})$ fixing the
    points $y_{1}, y_{2}$ acts on the $\P^{4}$ of conics passing
    through $y_{2}$. Let $G \subset H$ denote the stabilizer of $C$,
    viewed as a conic through $y_{2}$.  We will now show that $|G|=2$,
    from which the lemma follows.

    Any automorphism $h \in H$ preserving $C$ must fix the three
    points $y_{1},y_{2}$ and the point
    $y_{3}:= (\overline{y_{1},y_{2}} \cap C) \setminus \{y_{2}\}.$
    Therefore, $h$ must also fix $p := \Pole(y_{2},y_{3}) \in \P^{2}$.
    At the same time, $h$ must preserve the un-ordered pair of points
    $\Polar(y_{1}) \subset C$. It is now a simple exercise to see that
    there is a unique involution on $\P^{2}$ fixing $p$, preserving
    $C$ and interchanging the points of $\Polar(y_{1})$. Hence
    $|G|=2$, as desired.
  \end{proof}




\subsection{Goodness}
\label{sec:goodness1}

\begin{proposition}
  \label{prop:B1good}
  The family $\pi: X \to B_1$ is good.
\end{proposition}

\begin{proof}
  We use \autoref{prop:good}. If $[Z] \in B_{1}$ is any point,
  corresponding to a length $4$ subscheme $Z \subset C$, we
  immediately get a length $6$ admissible subscheme (see \cite[] )
  $Z' \subset \P^2$ by the rule
  \begin{align*}
    Z' = (Z+y_2) \cup \{y_{1}\}.
  \end{align*}
  Here, we view $C$ as a conic in $\P^{2}$ containing $y_{2}$, and the
  sum in $Z + y_{2}$ is as divisors on $C$.  The cubic surface
  $X_{[Z]} = \pi^{-1}([Z])$ is the same as the cubic surface $X_{Z'}$
  associated to $Z'$.

  In order to use \autoref{prop:good}, we next verify that the group
  $\Aut(\P^{2},Z')$ is finite.  First observe that $C \subset \P^{2}$
  must be the unique conic containing the length $5$ subscheme
  $ Z + y_{2} \subset Z'$.  Therefore, any element
  $h \in \Aut(\P^{2},Z')$ must preserve $C$.  As $y_{1}$ does not lie
  on $C$, we conclude that $h(y_{1}) = y_{1}$, and therefore $h$ must
  preserve the pair of points $\Polar(y_{1}) \subset C$. Furthermore,
  if we assume $h$ also fixes $y_{2}$, which we can do by passing to
  the connected component of the identity element in
  $\Aut(\P^{2},Z')$, then $h$ would have to preserve three distinct
  points on $C$, from which finiteness follows.
\end{proof}


\subsection{Relation}
\label{sec:relation}

The results in this section, taken together, yield the following
relation on the indetermined coefficients in \eqref{eq:P}:
  

\begin{align}
  \label{eq:relation1}
  16 \cdot a_{1^4} + 4 \cdot a_{1^2 2} + a_{2^2} = 72 \times \frac{6!}{4!} \times 2 = 4320.
\end{align}

\section{Family $B_2$}
\label{sec:family-b_2}


This section constructs and analyzes a good family over the base
$$B_2 := \overline{\M}_{0,7}.$$
To avoid unnecessary accumulation of symbols, we reset notation such
as $C,S,X, \dots$ from previous sections, and start anew.



Before diving into details, we summarize the construction. Let
$C \subset \P^{2}$ be a smooth conic with $7$ distinct marked points
$p_{0}, p_{1}, \dots, p_{5}, p_{\infty}$ on $C$, and let
$q \in \P^{2} \setminus C$ denote the intersection point of the
tangent lines of $C$ at $p_{0}$ and $p_{\infty}$, i.e.
$q = \Pole(p_{0},p_{\infty})$.  Then the scheme
$Z := \{p_{1}, \dots , p_{5}, q \}$ is an admissible length $6$
subscheme of $\P^{2}$, and its associated cubic surface $X_{Z}$ has a
finite automorphism group.  The main objective of this section is to
demonstrate how this construction {\sl can be extended over the
  boundary of $\overline{\M}_{0,7}$, yielding a good family of cubic
  surfaces.}

\subsection{Basics of $\overline{\M}_{0,7}$}
\label{sec:basics-overlinem_0-7}

We denote a general stable $7$-pointed genus zero curve by
$$(C, p_{0}, p_{1}, \dots, p_{5}, p_{\infty}),$$
and we let 
\begin{align}
  \label{eq:PM07}
  \varphi: \mathcal{C} \to \overline{\M}_{0,7}
\end{align}
denote the universal stable curve, with universal marking sections
denoted $$\sigma_{0}, \dots, \sigma_{\infty} \subset \mathcal{C}.$$

We let $\mathbf{L}$ denote the line bundle
$\O_{\mathcal{C}}(-\sigma_{\infty})|_{\sigma_{\infty}} \simeq
\omega_{\varphi}|_{\sigma_{\infty}}$ -- we view it as a line bundle on
$\overline{\M}_{0,7}$, as is customary.  Following standard notation,
we set $\psi_{\infty} := c_{1}\mathbf{L}$.  The sole enumerative
result about $\overline{\M}_{0,7}$ we will use in this section is:

\begin{theorem}[ \cite[]]
  \label{theorem:psi}
  $\int_{\overline{\M}_{0,7}} \psi_{\infty}^{4} = 1$.
\end{theorem}

\subsection{Construction of the family}
\label{sec:construction-familyB2}


We move on to the construction of our good family over $B_2$. Consider
the rank $2$ vector bundle
$$\mathcal{A} := \varphi_{*}\O_{\mathcal{C}}(\sigma_{\infty})$$ on
$\overline{\M}_{0,7}$.  From the fact that the line bundle
$\O_{\mathcal{C}}(\sigma_{\infty})$ restricts to $\mathbf{L}^{-1}$ on
$\sigma_{\infty}$ and $\O_{\sigma_{0}}$ on $\sigma_{0}$, it follows
that
\begin{align*}
  \mathcal{A} \simeq \O_{\overline{\M}_{0,7}} \oplus \mathbf{L}^{-1}.
\end{align*}

Next, put $\overline{\mathcal{C}} := \P \mathcal{A}^{\smvee}$;
$\overline{\mathcal{C}}$ is a $\P^{1}$-bundle over
$\overline{\M}_{0,7}$, and the surjection
$\varphi^{*}\mathcal{A} \to \O_{\mathcal{C}}(\sigma_{\infty})$ induces
a {\sl contraction map}

\begin{align}
  \label{eq:contract}
  \gamma: \mathcal{C} \to \overline{\mathcal{C}}.
\end{align}

The effect of $\gamma$ on a stable curve $(C, p_0, \dots, p_{\infty})$
is to contract all irreducible components not containing the marked
point $p_{\infty}$, leaving the unique $\P^{1}$ containing the marked
point $p_{\infty}$.  This remaining $\P^{1}$ is the corresponding
fiber of the $\P^{1}$-bundle $\overline{\mathcal{C}}$.

Under $\gamma$, the sections $\sigma_{i}$ map to sections
$\overline{\sigma_{i}}$ of $\overline{\mathcal{C}}$ over
$\overline{\M}_{0,7}$.  These sections have the following properties:
\begin{itemize}
\item $\overline{\sigma}_{\infty}$ is disjoint from all other sections, and
\item the union of all seven sections is supported on at least three
  points in every fiber of $\overline{\mathcal{C}}$ over
  $\overline{\M}_{0,7}$.
\end{itemize}




The next step is to invoke the relative $2$-veronese embedding
$$\iota: \overline{\mathcal{C}} \hookrightarrow \P \Sym^{2}\mathcal{A}^{\smvee}.$$ In this way, $\overline{\mathcal{C}} \subset \P \Sym^{2}\mathcal{A}^{\smvee}$ is a
family of smooth conics with $7$ marked points
$\overline{\sigma}_{0}, \dots, \overline{\sigma}_{\infty}$ satisfying
the two properties just mentioned.

\begin{definition}
  \label{def:tau} Let $\tau \subset \P \Sym^{2} \mathcal{A}^{\smvee}$
  denote the section obtained by taking the point polar, with respect
  to the conic $\overline{\mathcal{C}}$, to the line spanned by
  $\overline{\sigma}_{0}$ and $\overline{\sigma_{\infty}}$ in each
  fiber.
\end{definition}

\begin{lemma}
  \label{lemma:tau}
  The section $\tau$ is induced by an inclusion of the form
  ${\bf L}^{-1} \hookrightarrow \Sym^{2} \mathcal{A}^{\smvee}$.
\end{lemma}



\section{Family $B_3$}
\label{sec:family-b_3}

We construct our third family $B_3$ be starting with a quintic del
Pezzo surface $S$, which is the blow up of the plane at four general
points, and then ``blowing up all pairs of points on $S$.''

The surface $S$ has $10$ exceptional lines $L_{1}, \dots, L_{10}$.  We
let $S^{[2]}$ denote the Hilbert scheme of pairs of points on $S$.
$S^{[2]}$ contains $10$ disjoint $\P^{2}$'s,
$\Lambda_1, \dots, \Lambda_{10}$, namely the Hilbert schemes of pairs
of points contained in the lines $L_{i}$. Let
$\Lambda = \cup_{i}\Lambda_{i}$.

\subsection{Construction of $B_3$}
\label{sec:construction-b_3}

Let $Z \subset S^{[2]} \times S$ denote the universal degree two
subscheme; $Z$ is smooth and the first projection
$\pi_1 : Z \to S^{[2]}$ is finite, flat, and has degree two.



First, observe that the open set
\begin{align}
  \label{eq:UB3}
  U := S^{[2]} \setminus \Lambda
\end{align}
supports a good family of cubic surfaces, namely
\begin{align}
  \label{eq:XUB3}
  X^{\circ} := \Bl_{Z}(S^{[2]} \times S).
\end{align}

(We encourage the reader to check that $X^{\circ}/U$ is indeed good.)

However, when we extend $X^{\circ}$ in the natural way over $S^{[2]}$
the family acquires bad fibers, namely unions of quadrics and planes,
and therefore we must modify $S^{[2]}$ along $\Lambda$.

Let
\begin{align}
  \label{eq:S2tilde}
  \widetilde{S^{[2]}} := \Bl_{\Lambda}S^{[2]}
\end{align}
denote the blow-up with blow-down map
$\beta: \widetilde{S^{[2]}} \to S^{[2]}$.  Let
$E_{i} = \beta^{-1}(\Lambda_{i})$, $i=1, \dots, 10$ denote the
components of the of the exceptional divisor of the blow-up; $\beta$
expresses $E_{i}$ as a $\P^{1}$-bundle over $\Lambda_{i}$.

Next, let $\widetilde{Z} := \widetilde{S^{[2]}} \times_{S^{[2]}} Z$
denote the fiber-product; $\widetilde{Z}$ is a closed subscheme of the
product $\widetilde{S^{[2]}} \times S$, and is a finite, flat, degree
two cover of $\widetilde{S^{[2]}}$ under the first projection
$\tilde{\pi}_{1} : \widetilde{Z} \to \widetilde{S^{[2]}}.$

Inside the product $\widetilde{S^{[2]}} \times S$ we define the
smooth, closed subschemes
\begin{align}
  \label{eq:Fi}
  F_{i} := E_{i} \times L_{i};
\end{align}
we let $F := \cup_{i}F_{i}$.  We perform one more blow-up to get 
\begin{align}
  \label{eq:Xtilde}
  Y := \Bl_{F}\widetilde{S^{[2]}} \times S.
\end{align}
The natural projection $ Y \to \widetilde{S^{[2]}}$ is a family of
surfaces with simple normal crossing singular fibers over $E_{i}$.
The next lemma is critical.

\begin{lemma}
  The closed immersion
  $\widetilde{Z} \subset \widetilde{S^{[2]}} \times S$ lifts to a
  closed immersion $\widetilde{Z} \subset Y$.
\end{lemma}

\begin{proof}
  The main observation is that we have an equality of schemes
  \begin{align}
    \label{eq:Cartier}
    F_i \cap \widetilde{Z} = \widetilde{\pi}_{1}^{-1}(E_i) \cap \widetilde{Z}
  \end{align}
  for all $i=1, \dots, 10$, {\sl and therefore $F \cap \widetilde{Z}$
    is a Cartier divisor on $\widetilde{Z}$}. The claim now follows
  from a basic property of blow-ups.
\end{proof}



We are close to describing a family of cubic surfaces over
$\widetilde{S^{[2]}}$.  We first let
\begin{align}
  \label{eq:XB3}
  Y' := \Bl_{\widetilde{Z}}Y
\end{align}
denote the blow-up,
\begin{align}
  \label{eq:phiB3}
  \varphi: Y' \to Y
\end{align}
the blow-down map, and
\begin{align}
  \label{eq:piB3}
  \pi: Y' \to \widetilde{S^{[2]}}
\end{align}
the natural projection. Finally, let $F' \subset Y'$ denote the
exceptional divisor $\varphi^{-1}(F)$.
\begin{proposition}
  \label{proposition:resolv-b3}
  There exists a line bundle $\mathcal{L}$ on $Y'$ which induces a
  rational map
  \begin{align*}
    \rho: Y' \dashrightarrow \P(\pi_{*}\mathcal{L})
  \end{align*}
  whose image $X \subset \P(\pi_{*}\mathcal{L})$ is a good family of
  cubic surfaces over $\widetilde{S^{[2]}}$ with natural bundle
  $V = \pi_{*} \mathcal{L}$.
\end{proposition}

(By image, we mean ``closure of image''.)

(This one I still am confident in -- one simple blow-up resolves the situation.)


\subsection{Relation $B_3$}
\label{sec:relation-b_3}

The relation we get from family $B_3$ ultimately appears to be:
\begin{align}
  \label{eq:relationB3}
  6a_{1^{4}} + 21a_{1^{2}2}+6a_{13}+16a_{2^{2}}+a_{4} = 36 \times 6! = 25920.
\end{align}

(There is an 80 percent chance I made a mistake in the long
calculation, so be careful.)

\section{Family $B_4$}
\label{sec:family-b_4}

For this family, we fix a degree $6$ del Pezzo surface $S$, the blow
up of the plane at three non-collinear points, and then we fix a
general ``line'' (which is really a twisted cubic) $L$ in $S$ disjoint
from the three points blown up.  An open subset $U$ of the variety
$L \times L \times S$ carries a good family of cubic surfaces in the
obvious way. However, as in the case of $B_3$, the complement of $U$
is a union of surfaces which need to be blown up before obtaining a
good family of cubic surfaces.


\section{Family $B_5$}
\label{sec:family-b_5-1}

This family is similar to $B_1$. Fix a degree $7$ del Pezzo surface
$S$, and let $D \subset S$ denote a general hyperplane section; $D$ is
a degree $7$ elliptic normal curve.  Next observe that any degree four
subscheme $Z \subset D$ imposes independent conditions on sections of
$O_{S}(1)$, and that $\langle Z \rangle \cap S = Z$.  Furthermore, for
each $Z$, the projection map
$p_{\langle Z \rangle}: S \dashrightarrow \P^{3}$ has as image an
irreducible cubic, with finite automorphism group (check this!).


Therefore, the Hilbert scheme $B_{5} = D^{[4]}$ carries a good family
of cubic surfaces.  (The reason I like this family is that, unlike
$B_1$'s case, the natural bundle $V$ has more non-trivial chern
classes. Therefore, the relation we get this time is probably not the
same as for $B_1$.

\subsection{Difficulty with $B_5$}
\label{sec:difficulty-with-b_5}

The main obstacle in using this simple family is: I do not a priori
know the cubic surface count!!!
\section{Isotrivial family of surface with 3 $A_2$ singularities}
\label{sec:isotrivial3A2}

We outline the idea and give references, in order to fill in the computation relating to \eqref{eq:equality} later. 

Our starting point is the following fact:
\begin{proposition}
\label{prop:3A2}
The cubic surface defined by $X^3 + YZW = 0$ has singularity type $3A_2$ and is semistable.
\end{proposition}

\begin{remark}
\cite[Proposition 2.2]{N05} shows that the most special singularity types that correspond to semistable surfaces are $3A_2$ and $4A_1$. 
\end{remark}

\begin{proof}
The fact that $X^3 + YZW=0$ has singularity type $3A_2$ follows from \cite[Proof of 3.1.12]{N00}. Semistability follows from \cite[Proposition 2.3]{N05}.
\end{proof}

Given \autoref{prop:3A2}, we summarize the two facts about the $3A_2$ cubic surface that makes this family work:
\begin{proposition}
\label{prop:twofacts}
The cubic surface defined by $X^3 + YZW = 0$ has a nontrivial torus stabilizer and is not in the orbit closure of any stable cubic surface.
\end{proposition}

\begin{remark}
I think that this cubic surface is the most special surface that has a nontrivial torus stabilizer but is still semistable, which is means this method of finding a twisted isotrivial family of surfaces missing the general orbit closure only works for exactly this $3A_2$ surface. 
\end{remark}

\begin{proof}
The fact that the $3A_2$ cubic surface does not lie in the general cubic surface orbit closure follows for GIT. Indeed, we have the map $\pi: \mathbb{P}^{19}\dashrightarrow \mathbb{P}^{19}//PGL_4$ and by definition of semistability, the point defined by $X^3 + YZW = 0$ is not contained in its indeterminacy locus. After removing the indeterminancy locus, orbits of stable points are fibers of $\pi$, so they cannot contain the point defined by $X^3 + YZW = 0$. {\color{red} add GIT references to make sure}
\end{proof}

Finally, we obtain our test family:
\begin{proposition}
\label{prop:isotrivialfamily}
Given a base $B$ and line bundles $L_X, L_Y, L_Z, L_W$ such that $L_X^{\otimes 3}\cong L_Y\otimes L_Z\otimes L_W$, we can form the projective bundle $\mathbb{P}(L_X\oplus L_Y\oplus L_Z\oplus L_W)$. Inside of $\mathbb{P}(L_X\oplus L_Y\oplus L_Z\oplus L_W)$ we have the cubic surface $\mathcal{X}$ defined by $\{X^3 + YZW = 0\}$ over each trivialization of $L_X, L_Y, L_Z, L_W$ over $B$. Because $L_X^{\otimes 3}\cong L_Y\otimes L_Z\otimes L_W$, the cubic surface glues compatibly under transition maps.

The family $\mathcal{X}\to B$ is a nontrivial family of cubic surfaces where no member is a contained in the orbit closure of a stable cubic surface.
\end{proposition}

Thus, \autoref{prop:isotrivialfamily} affords an enumerative problem whose answer is zero. We worked with a general base $B$, but it suffices for our purposes to let $B=\mathbb{P}^4$. 

{\color{red} I suspect we can relate this to a collection of 6 points on $P^2$ with a stabilizer, so this family looks more like Anand's many families. From \cite[Proposition 3.3]{N05}, it looks like the length 6 scheme corresponding to the $3A_2$ surface is the intersection of the union of two lines with a triple line. Don't see it yet, but writing this down to not forget.}

\subsection{Isotrivial Relation}
\label{sec:isotrivial-relation}

The relation we obtain from Dennis's trick appears to be:

\begin{align}
  \label{eq:relationDennis}
  a_{2^{2}} = 0.
\end{align}

\section{More isotrivial families}
In this section, we exhibit a number of good isotrivial families.
All of these families will arise from a cubic surface $X$ with automorphism group $\mathbb G_m$.
To make sure that these families are good, we must prove that $X$ does not lie in the closure of the orbit of a generic cubic surface.
If $X$ is a semi-stable point of the $\SL_4$ action on the space of cubics $\P^{19}$, then this follows from GIT.
We now explain an extension of this idea that allows for even more examples.

Let $V$ be a 4-dimensional vector space.
Consider the natural action of $\SL(V)$ on $\P(\Sym^3V) \times \P V$ (here $\P$ denotes the space of one-dimensional subspaces).
That is, consider the action of $\SL_4$ on the set of pairs $(X, H)$, where $X \subset \P^3$ is a cubic surface and $H \subset \P^3$ is a hyperplane.
For a pair of positive integers $a, b$, the action lifts uniquely to an action on the ample line bundle $\mathcal O(a)\boxtimes \mathcal O(b)$; the GIT of the resulting linearized action depends only on the ratio $t = a/b$.

\begin{proposition}\label{prop:nolimit}
  Let $t$ be a positive rational number.
  Suppose $S \subset \P^3$ is a cubic surface such that for every hyperplane $H$, the pair $(S,H)$ is $t$-stable.
  Let $X \subset \P^3$ be a cubic surface with stabilizer group $\mathbb G_m \subset \SL_4$ such that for some $\mathbb G_m$-fixed hyperplane $H \subset \mathbb P^3$, the pair $(X, H)$ is $t$-semistable.
  Then $X$ does not lie in the closure of the $\SL_4$-orbit of $S$.
\end{proposition}
\begin{proof}
  Suppose $X$ lies in the orbit closure of $S$.
  Then there exists a one-parameter subgroup $\alpha \colon \mathbb G_m \to \SL_4$ and a cubic surface $Y \subset \P^3$ such that $Y$ is in the $\SL_4$-orbit of $S$ and
  \[ \lim_{t \to 0} \alpha_t(Y) = X.\]
  Since the stabilizer of $X$ is assumed to be a particular $\mathbb G_m \subset \SL_4$, the map $\alpha$ must factor through this $\mathbb G_m \subset \SL_4$.
  Consider the $\alpha$-fixed hyperplane $H \subset \P^3$ such that $(X, H)$ is $t$-semistable.
  We have
  \[ \lim_{t \to 0} \alpha_t(Y, H) = (X, H).\]
  This contradicts that $(Y, H)$ is $t$-stable.
\end{proof}
\begin{corollary}\label{cor:nolimit}
  Let $X$ be as in \autoref{prop:nolimit} and assume $0 < t \leq 3/7$.
  Let $S$ be a smooth cubic surface without an Eckardt point.
  Then $X$ is not in the closure of the $\SL_4$ orbit of $S$.
\end{corollary}
\begin{proof}
  We use the classification of $t$-stable pairs $(S,H)$ due to Gallardo and Martinez-Garcia \cite{gal.mar:19}.
  For a smooth cubic surface $S$ without an Eckardt point and any hyperplane $H$, the curve $D = S \cap H$ is reduced and has $A_n$ singularities for $n \leq 3$ (at worst tacnodes).
  From \cite[Theorem~2]{gal.mar:19}, it follows that $(S, H)$ is $t$-stable.
  We now use \autoref{prop:nolimit}.
\end{proof}

\begin{corollary}
  The following surfaces with stabilizer $\mathbb G_m \subset \SL_4$ are not in the closure of the $\SL_4$-orbit of a generic cubic surface (the parenthesis describes the singularities):
  \begin{enumerate}
  \item $x_0x_1x_3 = x_2^3$ \quad $(3A_2)$
  \item $x_3(x_0x_2-x_1^2) = x_0x_1^2$ \quad $(A_3 + 2A_1)$
  \item $x_3(x_0x_2-x_1^2) = x_0^2x_1$ \quad $(A_4 + A_1)$
  \item $x_3x_0^2 = x_1^3 + x_2^3$ \quad $(D_4)$
  \end{enumerate}
\end{corollary}
\begin{proof}
  Together with a suitable $\mathbb G_m$-invariant hyperplane section $H$, these surfaces are $t$-semistable for $0 < t < 1$, $t = 1/5$, $t = 1/3$, and $t = 3/7$, respectively (\cite[Table~2]{gal.mar:19}).
  We now apply \autoref{cor:nolimit}.
\end{proof}

Let $X$ be a good cubic surface (not in the closure of a general orbit) with stabilizer group $\mathbb G_m$.
We have a good family
\[ \mathcal X = [X / \mathbb G_m] \xrightarrow{\pi} [. / \mathbb G_m] = B\mathbb G_m,\]
yielding a moduli map
\[\mu \colon B \mathbb G_m \to [\mathbb P^{19}/\SL_4].\]
By construction, the pull-back under $\mu$ of the closure of a generic orbit is empty.
Therefore, we must have
\[ a_{1^4} v_1^4 + a_{1^22}v_1^2v_2 + a_{13}v_1v_3 + a_{2^2}v_2^2 + a_4v_4 = 0.\]
By computing $v_1^4, \dots, v_4$, we get a linear relationship among the coefficients.

To compute $v_1^4, \dotso, v_4$, we must identify the vector bundle $\pi_* \left( \omega_{\mathcal X/B\mathbb G_m}^{-1}\right)$.
To do so, let $\mathcal V$ be the rank 4 vector bundle on $B \mathbb G_m$ corresponding to the representation $\mathbb G_m \to \SL_4$.
Then $\mathcal X \subset \P \mathcal V$ is a divisor, given by a global section of a line bundle
\[ \mathcal L = \mathcal O_{\P \mathcal V}(3) \otimes \pi^* M\]
for some line bundle $M$ on $B\mathbb G_m$.
By adjunction, we have
\begin{align*}
  \omega_{\mathcal X/B\mathbb G_m} &= \omega_{\P \mathcal V / \mathbb G_m} \otimes \mathcal L \big|_{\mathcal X}\\
                                   &= \mathcal O_{\P \mathcal V}(-4) \otimes \mathcal O_{\P \mathcal V}(3) \otimes \pi^* M \big|_{\mathcal X} \\
                                   &= \mathcal O_{\P \mathcal V}(-1) \otimes \pi^* M \big |_{\mathcal X},
\end{align*}
and hence
\begin{align*}
  \pi_* \left( \omega_{\mathcal X/B\mathbb G_m}  \right) &= \pi_* \left( \mathcal O_{\P \mathcal V}(1) \big|_{\mathcal X} \right) \otimes M^\vee \\
  &= \mathcal V \otimes M^\vee.
\end{align*}
Hence, by identifying $\mathcal V$ and $M$, we can easily compute the chern classes $v_i$.

Given $a \in \mathbb Z$, we denote by $\chi(a)$ the line bundle on $B\mathbb G_m$ corresponding to the character $t \mapsto t^a$.
Denote by $q \in A^1(B\mathbb G_m)$ the generator of the cohomology ring given by $q = c_1(\chi(1))$.
\subsection{The family $3A_2$}
For
\[ X: x_0x_1x_3 = x_2^3\]
a stabilizing $\mathbb G_m \subset \SL_4$ is given by the diagonal matrix with exponents $(a,b,0,c)$ where $a+b+c = 0$.
Thus, we have
\[\mathcal V = \chi(a) \oplus \chi(b) \oplus \chi(0) \oplus \chi(c).\]
The element $x_0x_1x_3 - x_2^3$ is a global section of $\Sym^3 \mathcal V$.
In other words, $\mathcal X$ is a section of $\mathcal O_{\P \mathcal V}(3)$ and hence we have
\[ M = \chi(0).\]
We get
\[ v_1 = 0, \quad v_2 = (ab+bc+ca) \cdot q^2, \quad v_3 = abc \cdot q^3, \quad v_4 = 0,\]
and hence
\[ v_1^4 = 0, \quad v_1^2v_2 = 0, \quad v_1v_3 = 0,\quad v_2^2 \neq 0, \quad v_4 = 0.\]
Therefore, this family gives the relation
\begin{equation}\label{eqn:iso1}
  a_{2^2} = 0.
\end{equation}

\subsection{The family $A_3 + 2A_1$}
For
\[ X: x_3(x_0x_2-x_1^2) = x_0x_1^2,\]
the stabilizing $\mathbb G_m \subset \SL_4$ is given by the diagonal matrix with exponents $(-3,1,5,-3)$.
Thus, we have
\[ \mathcal V = \chi(-3) \oplus \chi(1) \oplus \chi(5) \oplus \chi(-3).\]
The element $x_3(x_0x_2-x_1^2) - x_0x_1^2$ defines a global section of $\Sym^3 \mathcal V \otimes \chi(1)$.
In other words, we have
\[ M = \chi(1).\]
%((-4 -16 64 0) (256 -256 -256 256 0))
We get
\[ v_1 = -4q, \quad v_2 = -16q^2, \quad v_3 = 64q^3, \quad v_4 = 0,\]
and hence
\[ v_1^4 = 256 \quad v_1^2v_2 = -256, \quad v_1v_3 = -256, \quad v_2^2 = 256, \quad v_4 = 0.\]
Therefore, this family gives the relation
\begin{equation}\label{eqn:iso2}
  a_{1^4} - a_{1^2 2}- a_{13} +  a_{2^2}  = 0.
\end{equation}

\subsection{The family $A_4 + A_1$}
For
\[ X: x_3(x_0x_2-x_1^2) = x_0^2x_1,\]
the stabilizing $\mathbb G_m \subset \SL_4$ is given by the diagonal matrix with exponents $(1,-1,-3,3)$.
Thus, we have
\[ \mathcal V = \chi(1) \oplus \chi(-1) \oplus \chi(-3) \oplus \chi(3).\]
The element $x_3(x_0x_2-x_1^2) - x^2_0x_1$ defines a global section of $\Sym^3 \mathcal V \otimes \chi(-1)$.
In other words, we have
\[ M = \chi(-1).\]
We get
\[ v_1 = 4q, \quad v_2 = -4q^2, \quad v_3 = -16q^3, \quad v_4 = 0,\]
and hence
\[ v_1^4 = 256 \quad v_1^2v_2 = -64, \quad v_1v_3 = -64, \quad v_2^2 = 16, \quad v_4 = 0.\]
Therefore, this family gives the relation
\begin{equation}\label{eqn:iso3}
  16a_{1^4} -4a_{1^2 2}- 4a_{13} + 1 a_{2^2}  = 0.
\end{equation}

\subsection{The family $D_4$}
For
\[ X: x_3x_0^2 = x_1^3+x_2^3,\]
the stabilizing $\mathbb G_m \subset \SL_4$ is given by the diagonal matrix with exponents $(5,1,1,-7)$.
Thus, we have
\[ \mathcal V = \chi(5) \oplus \chi(1) \oplus \chi(1) \oplus \chi(-7).\]
The element $x_3x_0^2-x_1^3-x_2^3$ defines a global section of $\Sym^3 \mathcal V \otimes \chi(-3)$.
In other words, we have
\[ M = \chi(-3).\]
We get
\[ v_1 = -12q, \quad v_2 = -16q^2, \quad v_3 = 192q^3, \quad v_4 = -512q^4,\]
and hence
\[ v_1^4 = 20736 \quad v_1^2v_2 = 2304, \quad v_1v_3 = -2304, \quad v_2^2 = 256, \quad v_4 = -512.\]
Therefore, this family gives the relation
\begin{equation}\label{eqn:iso4}
  81a_{1^4} +9a_{1^2 2}- 9a_{13} +  a_{2^2}-2a_4  = 0.
\end{equation}

\subsection{Families over a base variety}
By choosing a suitable base $B$ and a map $B \to B \mathbb G_m$, we can construct an isotrivial family over $B$ by pulling back one of the families above.
We describe this explicitly in an example.

Let $B = \mathbb P^4$.
Set
\[V = \mathcal O(5) \oplus \mathcal O(1) \oplus \mathcal O(1) \oplus \mathcal O(-7).\]
Let $x_0, x_1, x_2, x_3$ be generators of the four summands on the standard $\mathbb A^4 \subset \mathbb P^4$.
We have the section $(x_3x_0^2-x_1^3-x_2^3)$ of $\Sym^3 V = \mathcal O(3)^{\oplus 20}$.
Note that this section has a pole of order $3$ along the hyperplane at infinity.
As a result, it defines a section $\xi$ of $\Sym^3 V \otimes \mathcal O(-3)$, which is nowhere vanishing.
Equivalently, $\xi$ is a section of $\mathcal O_{\P V}(3) \otimes \pi^* \mathcal O(-3)$.
Our family $\mathcal X \to B$ is defined by the zero-locus of $\xi$ in $\P V  \to B$.

\appendix

\section{Existance of a universal formula}

In this section, we recall statements from equivariant intersection theory that guarantee the existence of the formula \eqref{eq:P}. On this first pass, we will let $\mathbb{P}(V)$ denote the projective bundle of 1-dimensional subspaces in the fibers of $V$ and correct for the sign later if people want to work with duals. 

\begin{lemma}
\label{lem:Q_Zclass}
Let $W$ be an $r+1$-dimensional vector space and $Z\subset \operatorname{Sym}^d W^{\vee}$ be a subvariety. Then, the equivariant class $[\mathbb{P}Z]$ inside the equivariant Chow ring 
\begin{align}
    A^{\bullet}(\mathbb{P}_{GL_{r+1}}(\operatorname{Sym}^d W^{\vee}))\cong \frac{\mathbb{Z}[H, t_0,\ldots,t_{r}]^{S^{r+1}}}{\left(\displaystyle\prod_{\substack{i_0+\cdots+i_{r}=d\\ i_0,\ldots,i_r\geq 0}}(H-i_0 t_0 - \cdots - i_r t_r)\right)}\label{eq:equivariantSym}
\end{align}
can be expressed as
\begin{align*}
    Q_Z(t_0-\frac{H}{d},\ldots,t_{r}-\frac{H}{d}),
\end{align*}
for polynomial homogeneous $Q_Z$ with degree equal to the codimension of $Z$. 
\end{lemma}

The variables $t_i$'s in \autoref{lem:Q_Zclass} can either be viewed as chern roots or via the inclusion into the torus-equivariant Chow ring 
\begin{align*}
    A^{\bullet}(\mathbb{P}_{T}(\operatorname{Sym}^d W^{\vee}))\cong \frac{\mathbb{Z}[H, t_0,\ldots,t_{r}]}{\left(\displaystyle\prod_{\substack{i_0+\cdots+i_{r}=d\\ i_0,\ldots,i_r\geq 0}}(H-i_0 t_0 - \cdots - i_r t_r)\right)}
\end{align*}
where $T\subset GL_{r+1}$ is the standard torus.

\begin{proof}[Proof of \autoref{lem:Q_Zclass}]
The formula for the Chow ring of $A^{\bullet}(\mathbb{P}_{GL_{r+1}}(\operatorname{Sym}^d W^{\vee}))$ in \eqref{eq:equivariantSym} follows from the Chow ring of a projective bundle. %applied to the construction of an equivariant Chow ring, didn't find a quick reference for this than other people saying its obvious

The formula for $[\mathbb{P}Z]$ in terms of a polynomial $Q_Z$ follows from \cite[Theorem 6.1]{FNR05}, where $Q_Z$ is the formula for the class of $[Z]$ in $A^{\bullet}_{GL_r+1}(\operatorname{Sym}^d W^{\vee})\cong \mathbb{Z}[H, t_0,\ldots,t_{r}]$. 
\end{proof}

\begin{proposition}
In the context of \autoref{def:goodfamily} a universal polynomial $P$ as in \eqref{eq:P} exists.
\end{proposition}

\begin{proof}
Following the setup in \eqref{eq:P}, we start with a good family $\pi: X\to B$ and let $V=\pi_{*}\omega_{X/B}^{-1}$. Since each fiber of $X\to B$ is embedded into $\mathbb{P}(V)$ as a cubic surface via the anticanonical map, we get a section $\sigma$ of the bundle $\mathbb{P}(\operatorname{Sym}^3 V^{\vee})\to B$. The section $\sigma$ maps each point $b$ to the equation of the cubic surface $X_b$ lying above it.

Inside of $\mathbb{P}(\operatorname{Sym}^3 V^{\vee})$, the section $\sigma$ is induced by the inclusion of a line bundle $L=\det(V^{\vee})\hookrightarrow \operatorname{Sym}^3 V^{\vee}$. {\color{red} Check this, the main thing we need is that the line bundle can be expressed in terms of $c_1(V)$ only. I don't have a clean proof yet.}

Now, we apply \autoref{lem:Q_Zclass}, where $Z\subset \operatorname{Sym}^3(\mathbb{C}^{4\ast})$ is the $GL_4$ orbit closure of a general degree 3 homogenous equation in 4 variables. The vector bundle $V\to B$ induces a map $B\to [\operatorname{pt}/GL_4]$ under which $[\operatorname{Sym}^3(\mathbb{C}^{4\ast})/GL_4]$ pulls back to $\mathbb{P}(\operatorname{Sym}^3 V^{\vee})$. Under the pullback the equivariant class of the projectivized orbit closure $[\mathbb{P}Z]$ pulls back to the class of the relative orbit closure $\mathcal{Z}\subset \mathbb{P}(\operatorname{Sym}^3 V^{\vee})$, where each fiber of $\mathcal{Z}\to B$ is given by $Z$. By \autoref{lem:Q_Zclass}, the class of $\mathcal{Z}$ depends only on the chern classes of $V$. 

The polynomial $P$ in \eqref{eq:P} is the intersection number of $\sigma$ with the class of $\mathcal{Z}$. The class of $\sigma$, the Chow ring of $\mathbb{P}(\operatorname{Sym}^3 V^{\vee})$, and the class of $\mathcal{Z}$ are depend only on the chern classes of $V$. Thus, the final intersection number depends only on the chern classes of $V$ as desired. 
{\color{red} I don't think it'll be any harder to actually determine the formula of $P$ in \eqref{eq:P} in terms of the equivariant class of an orbit closure of a cubic surface, but we don't seem to need the formula. The point is that $P$ and the equivariant class of the orbit closure are equivalent by some substitution.}
\end{proof}

\section{Congruence relations from hypersurfaces with finite automorphisms}
As another another check for the class, I think we can get congruence relations from isotrivial families of hypersurfaces with finite linear automorphisms. This is the same idea as the $3A_2$ family, except the condition holds in $H_{G}(\operatorname{pt})$ with $G$ a finite group instead of $\mathbb{G}_m$. 

\begin{proposition}
\label{prop:isotrivial2}
Let $X\subset \mathbb{P}^r$ be a hypersurface with a linear automorphism group $G\subset \operatorname{Aut}(X)\subset GL_{r+1}$. Let $Q$ be the polynomial $Q_Z$ in \autoref{lem:Q_Zclass} where $Z$ \emph{any} equivariant cycle in the space of hypersurfaces not containing $X$. Then, under the linear representation $G\hookrightarrow GL_{r+1}$, $Q$ is sent to zero under the characteristic class map:
\begin{align*}
    A^{\bullet}_{GL_{r+1}}\cong \mathbb{Z}[t_0,\ldots,t_{r}]\to A^{\bullet}_{G}(\operatorname{pt}). 
\end{align*}
\end{proposition}

% \begin{proof}
% Continue: the key point is that the twisted family of hypersurfaces comes from descending a trivial section of Sym^d of the universal vector bundle pulled back from BG\to BGL_{r+1}, so intersecting this section with the orbit closure picks out constant term of the projective equivariant class. This constant term is exactly $Q$ in the proposition.

% This is just the general construction of the twisted family:
% Given a hypersurface $X\subset \mathbb{P}^r$ with a finite linear automorphism group $G=\operatorname{Aut}(X)\subset GL_{r+1}$, we want to construct a twisted version of $X$ over $BG$. To this end, take $X\times ((\mathbb{C}^{r+1})^N\backslash Z)\subset \mathbb{P}^r \times ((\mathbb{C}^{r+1})^N\backslash Z)$, where $N>>0$ and $Z$ is some closed set of high codimension. Here $G$ acts on $X$ and $\mathbb{P}^{r+1}$ by linear automorphisms and on each factor of $\mathbb{C}^{r+1}$ via $GL_{r+1}$. The closed set $Z$ is chosen to $G$ acts freely on $(\mathbb{C}^{r+1})^N\backslash Z$. 

% Taking the quotient by $G$ yields a nontrivial family of hypersurfaces $\mathcal{X}\to ((\mathbb{C}^{r+1})^N\backslash Z)/G$ inside the projectivization of some vector bundle $W$ over $((\mathbb{C}^{r+1})^N\backslash Z)/G$.
% \end{proof}
\begin{example}
\autoref{prop:isotrivial2} specializes to \autoref{sec:isotrivial3A2} when applied to the cubic surface $X^3=YZW$.
\end{example}

\begin{example}
Every coefficient of every class of a quartic plane curve we computed in \cite{LPT19} is divisible by 4 (even after dividing by the automorphism groups). I think this is a consequence of the Fermat quartic having automorphism group containing $(\mu_4)^3\hookrightarrow GL_3$. Similarly, every equivariant class of a cubic curve orbit is divisible by 3 in \cite[Appendix C]{LPT19}, and this should follow from the Fermat cubic. We will try to prove this in \autoref{prop:divd} below.
\end{example}

Given the example, we will try to flesh out the application of \autoref{prop:3A2} to the Fermat hypersurface applied to the case $G=(\mu_d)^{r+1}\subset GL_{r+1}$. In general, I don't know how to compute the map $A^{\bullet}_{GL_{r+1}}\to A^{\bullet}_{G}(\operatorname{pt})$ (google ``characteristic class of a linear representation''). 

\subsection{Fermat hypersurfaces}
A Fermat hypersurface $X\subset \mathbb{P}^r$ of degree $d$ has a linear automorphism group containing $(\mu_d)^{r+1}$. {\color{red} You can also permute the coordinates, curious what condition in $A^{\bullet}_{S_{r+1}}$ that gives...}

\begin{lemma}
\label{lem:mu_d}
Under the inclusion $\mu_d\hookrightarrow \mathbb{G}_m$, the map in group cohomology is given by 
\begin{align*}
    \mathbb{Z}[t]=A^{\bullet}_{\mathbb{G}_m}(\operatorname{pt})\to A^{\bullet}_{\mu_d}(\operatorname{pt})=\mathbb{Z}[t]/(dt)
\end{align*}
\end{lemma}

\begin{proof}
The ring structure of $A^{\bullet}_{\mu_d}(\operatorname{pt})$ is given by the cohomology ring of the Lens space 
\href{https://mathoverflow.net/questions/133974/reference-for-ring-structure-on-group-cohomology}{(mathoverflow link)}. To compute the map, we take an approximation of $B\mathbb{G}_m$ and $B\mu_d$ to compute the map in $A^{1}_{\mathbb{G}_m}(\operatorname{pt})\to A^{1}_{\mu_d}(\operatorname{pt})$. This reduces to a familiar geometric example of a cone over a rational normal curve.

We approximate using the map $B\mu_d\to B\mathbb{G}_m$ using
\begin{align*}
    \pi: S=\operatorname{Spec}(\mathbb{C}[x^d, x^{d-1}y,\ldots,y^d])=(\mathbb{A}^2\backslash\{0\})/\mu_d\to (\mathbb{A}^2\backslash\{0\})/\mathbb{G}_m=\mathbb{P}^1. 
\end{align*}
The map $\pi$ is the projection of the cone over a degree $d$ rational normal curve (minus the origin) onto the rational normal curve. The content of \autoref{lem:mu_d} is that a ruling of the cone $S$ over a rational normal curve generates the class group of the cone. 

This is true because $S\backslash L\cong \mathbb{A}^2$ where $L$ is a ruling. (The more nontrivial fact is that $A^{1}(S)\cong \mathbb{Z}/d\mathbb{Z}$, so $[L]$ is exactly $d$-torsion. This is implied by the cohomology of the lens space above, but one can probably prove it directly. For example, $[L]$ is nontrivial in the class group because it cannot be cut out by a single equation (since the tangent space at the cone is at least 3-dimensional for $d>1$).) 
\end{proof}

\begin{proposition}
\label{prop:divd}
If $Q$ is the polynomial associated to the equivariant class of \emph{any} equivariant class in the space of degree $d$ hypersurfaces not containing the Fermat hypersurface, then every coefficient of $Q$ is divisible by $d$.
\end{proposition}

\begin{proof}
This follows from \autoref{lem:mu_d} and \autoref{prop:isotrivial2}.
\end{proof}

\begin{example}
For a general cubic surface, our current guess is that:
$$Q = 25920 c_1^4+12960 c_1^2 c_2-6480 c_1 c_3+9720 c_4$$
 and
$$P = 1080 c_1^2 c_2-1080 c_1 c_3+9720 c_4,$$
where the $P$ and $Q$ are related by
\begin{align*}
P(t_0,t_1,t_2,t_3) &= Q(t_0 - \frac{t_0+\cdots+t_3}{3},\ldots, t_3 - \frac{t_0+\cdots+t_3}{3})\\
P(t_0 - (t_0+\cdots+t_3), \ldots, t_3 - (t_0+\cdots+t_3)) &= Q(t_0,\ldots,t_3)
\end{align*}
The coefficients of $Q$  are all divisible by 3 as predicted.
\end{example}
\bibliographystyle{plain}
\bibliography{references.bib}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

